Interval Probability for Fuzzy Quantum Theories

### 2016-05-11 prob.tex
prob.tex \subsection{Buffon's Needle Problem} verifying what I typed...

Suppose we drop a needle of length $\ell$ onto a floor made of equally
spaced parallel lines a distance $h$ apart. It is a known fact that
the probability of the needle crossing a line converges to
$\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
We analyze this situation in the mathematical framework of probability
spaces paying special attention to the resources needed to estimate
the probability computationally or experimentally.

To formalize the experiment, we consider an experimental setup
consisting of a collection of $N$ identical needles of length
$\ell$. We throw the $N$ needles one needle at a time, and observe the number
$X$ of needles that cross a line. The sample space can be expressed as the set
$\{X,-\}^N$
of sequences of characters of length $N$ where each character is
either $X$ to indicate a needle crossing a line or $-$ to indicate a
needle not crossing a line. If $N=3$, the probability of the event that exactly
2 needles cross lines~$\{-XX,X-X,XX-\}$ can be 
estimated by the relative frequency~$\frac{3}{8}$. Generally, the probability of
the event that exactly $M$ needles out of the $N$ total needles cross lines can
be estimated by the relative frequency~$\frac{M}{N}$.

In an actual experiment with $500$ needles and the ratio
$\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$ 
crossed a line so the relative frequency is $0.472$ comparing 
the values to the idealized mathematical probability $0.4775\ldots$. In a larger 
experiment with $5000$ needles and the ratio $\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, 
the relative frequency was calculated to be $0.5064$ comparing 
the values to the idealized mathematical probability $0.5093\ldots$. We see that 
the observed probability approaches $\frac{2\ell}{\pi h}$ but only if
\emph{larger and larger resources} are expended.

>>>>

Suppose we drop a needle of length $\ell$ onto a floor made of equally
spaced parallel lines a distance $h$ apart. It is a known fact that
the probability of the needle crossing a line is
$\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
We analyze this situation in the mathematical framework of probability
spaces paying special attention to the resources needed to estimate
the probability computationally or experimentally.

To formalize the experiment, we consider an experimental setup
consisting of a collection of $N$ identical needles of length
$\ell$. We throw the $N$ needles one needle at a time, and observe the number
$X$ of needles that cross a line. The sample space can be expressed as the set
$\{X,-\}^N$
of sequences of characters of length $N$ where each character is
either $X$ to indicate a needle crossing a line or $-$ to indicate a
needle not crossing a line. If $N=3$, the probability of the event that exactly
2 needles cross lines~$\{-XX,X-X,XX-\}$ can be 
estimated by the relative frequency~$\frac{2}{3}$. Generally, the probability of
the event that exactly $M$ needles out of the $N$ total needles cross lines can
be estimated by $\frac{M}{N}$.

In an actual experiment with $500$ needles and the ratio
$\frac{\ell}{h}=0.75$~\cite{Hall1873}, it was found that $236$ 
crossed a line so the relative frequency is $0.472$ comparing 
the values to the idealized mathematical probability $0.4774\ldots$. In a larger 
experiment with $5000$ needles and the ratio $\frac{\ell}{h}=0.8$~\cite{Uspensky1937}, 
the relative frequency was calculated to be $0.5064$ comparing 
the values to the idealized mathematical probability $0.5092\ldots$. We see that 
the observed probability approaches $\frac{2\ell}{\pi h}$ but only if
\emph{larger and larger resources} are expended.
